Binary companions of red clump stars

### 2017-07-31 paper/main.tex
equations

In addition to the above requirements, we make the following assumptions
that restrict our attention to a well-defined model space:
\begin{description}
\item[correct samplings] accurate representations of posterior pdf
  given prior and likelihood; correct likelihood function.
\item[no trinaries] related to the above: no trinaries, quads, or anything
  crazier.
\item[sufficent samplings] density and support of samplings
\item[independent stars] no relation between one star and another; each
  drawn from the same population; no multiple populations.
\item[population parameterization] whatevs
\end{description}

@@

Because all we have is a sampling of each system under the interim prior,
we have to re-weight or importance-sample the individual-star samplings
in this hierarchical inference... Cite Hogg et al; Cite DFM et al.

>>>>

In addition to the above requirements, we make the following assumptions
that restrict our attention to a well-defined model space:
\begin{description}
\item[correct samplings] accurate representations of posterior pdf
  given prior and likelihood; correct likelihood function. We hereby
  take on all the assumptions given in \sectionname~\ref{sec:fitting},
  about noise and kinematics, and so on.
\item[no trinaries] related to the above: no trinaries, quads, or anything
  crazier.
\item[sufficent samplings] density and support of samplings
\item[independent stars] no relation between one star and another; each
  drawn from the same population; no multiple populations.
\item[population parameterization] whatevs
\end{description}

@@

Because all we have is a sampling of each system under the interim prior
$p(\omega\given H_0)$,
we have to re-weight or importance-sample the individual-star samplings
in this hierarchical inference... Cite Hogg et al; Cite DFM et al.
% The following needs checking for symbol conventions
\begin{eqnarray}
  \ln p(y\given\alpha,H_1) &=& \sum_{n=1}^N \ln p(y_n\given\alpha,H_1)
  \\
  \ln p(y_n\given\alpha,H_1) &\propto& \ln\left[\frac{1}{K_n}\,\sum_{k=1}^{K_n}\frac{p(\omega_{nk}\given\alpha,H_1)}{p(\omega_{nk}\given H_0)}\right]
  \quad .
\end{eqnarray}
